---
title: "DataExploration"
author: "Avery Chan"
date: "10/30/2021"
output:
  html_document:
    toc: yes
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(hms)
theme_set(theme_bw())
```

## Read data

```{r}
data_Q_activity <- read_csv("1week/Qbserve_byactivity_2021-10-15_2021-10-23.csv", col_types = cols())
data_Q_hour <- read_csv("1week/Qbserve_byhour_2021-10-15_2021-10-23.csv", col_types = cols())
data_T_time <- read_csv("1week/Toggl_time_entries_2021-10-15_to_2021-10-22.csv", col_types = cols())
data_T_summary <- read_csv("1week/Toggl_Track_summary_report_2021-10-15_2021-10-22.csv", col_types = cols())

# calendar data
data_C_Avery <- read_csv("calendar/Avery.csv", col_types = cols())
data_C_Classes <- read_csv("calendar/Classes.csv", col_types = cols())
data_C_System <- read_csv("calendar/System.csv", col_types = cols())
data_C_TimeBlocks <- read_csv("calendar/Time_Blocks.csv", col_types = cols())
```

## Clean data

```{r}
# convert to time units
data_Q_hour <- data_Q_hour %>%
  mutate(Hour = parse_date_time(Hour, '%I %p') %>%
           # hour() %>%
           hms::as_hms())

data_T_time <- data_T_time %>%
  select(Project,
         Description,
         `Start date`,
         `End date`,
         `Start time`,
         `End time`,
         Duration)
data_T_summary <- data_T_summary %>%
  select(Project, Description, Duration)

# move long column so printing is better
data_Q_activity <-
  data_Q_activity %>% relocate(Name, .after = Category)

data_T_time <- data_T_time %>%
  mutate(Minutes = seconds(Duration) %>% as.numeric() / 60)
data_T_summary <- data_T_summary %>%
  mutate(Minutes = seconds(Duration) %>% as.numeric() / 60)

data_Q_activity
data_Q_hour
data_T_time
# data_T_summary
```

## Initial look at Qbserve data

```{r}
categories <- data_Q_activity %>%
  group_by(Category) %>%
  summarise(n = n(),
            Min = sum(Minutes)) %>%
  arrange(-Min)
# categories

app_usage <- data_Q_activity %>%
  group_by(App) %>%
  summarise(n = n(),
            Min = sum(Minutes)) %>%
  filter(Min > 5) %>%
  arrange(-Min)
# app_usage

categories %>% ggplot(aes(
  x = reorder(Category,-Min),
  y = Min,
  fill = n
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  ))

app_usage %>% ggplot(aes(
  x = reorder(App, -Min),
  y = Min,
  fill = n
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  ))
```

## Initial look at Toggl data

We learn that we can ignore `data_T_summary` since it encodes the same information as `data_T_time`.

```{r}
## Left over to parse
# data_Q_hour
# data_T_time
# data_T_summary

## Get the same information here
data_T_time_summary <- data_T_time %>% 
  group_by(Project, Description) %>% 
  summarise(
    Duration = sum(Duration) %>% hms::as_hms(),
    Minutes = sum(Minutes)
  )

# data_T_summary
# They are the same...
data_T_time$Duration %>% sum() == data_T_summary$Duration %>% sum()
```
First data just around categories.

```{r}
data_T_time_summary %>% 
  ggplot(aes(x = reorder(Project, Minutes), y = Minutes, fill=Description)) +
  geom_col()
```

Then data more temporally. (Calendar might go here)

```{r}
data_Q_hour
data_T_time
```

## Requirements

- Static visualization
- A legend that explains the encodings used
- 2-3 paragraphs explain your visualization and the insights that you gain about yourself by creating the visualization

I hoped to learn where my time went. Honestly, I already had the data collection heavily habituatilzed so that's why I chose it. Additionally, I partially kept up this record keeping because starting a timer incetivises me to work. In some way, it tells me that work has started.

I also noticed that I will start the timer to match when I start working. I don't know what this means, probably just that it's a habit. Honestly that's just motivated by the aspiration for more complete data.

I think more interesting would be a holistic overview that overlays what I did with my records. This would be calendar data and journaling information although I didn't really do that over this week.
























