---
title: "DataExploration"
author: "Avery Chan"
date: "10/30/2021"
output:
  html_document:
    toc: yes
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(hms)
theme_set(theme_bw())
library(r2d3)
bars <- c(10, 20, 30)
library(shiny)
```

```{d3 eval=FALSE, message=FALSE, warning=FALSE, data=bars, include=FALSE, list(color=, options=list(color = 'orange')}
svg.selectAll('rect')
  .data(data)
  .enter()
    .append('rect')
      .attr('width', function(d) { return d * 10; })
      .attr('height', '20px')
      .attr('y', function(d, i) { return i * 22; })
      .attr('fill', options.color);
```

## Read data

```{r}
data_Q_activity <- read_csv("1week/Qbserve_byactivity_2021-10-15_2021-10-23.csv", col_types = cols())
data_Q_hour <- read_csv("1week/Qbserve_byhour_2021-10-15_2021-10-23.csv", col_types = cols())
data_T_time <- read_csv("1week/Toggl_time_entries_2021-10-15_to_2021-10-22.csv", col_types = cols())
data_T_summary <- read_csv("1week/Toggl_Track_summary_report_2021-10-15_2021-10-22.csv", col_types = cols())

# calendar data
data_C_Avery <- read_csv("calendar/Avery.csv", col_types = cols())
data_C_Classes <- read_csv("calendar/Classes.csv", col_types = cols())
data_C_System <- read_csv("calendar/System.csv", col_types = cols())
data_C_TimeBlocks <- read_csv("calendar/Time_Blocks.csv", col_types = cols())
```

## Clean data

```{r}
# convert to time units
data_Q_hour <- data_Q_hour %>%
  mutate(Hour = parse_date_time(Hour, '%I %p') %>%
           # hour() %>%
           hms::as_hms())

data_T_time <- data_T_time %>%
  select(Project,
         Description,
         `Start date`,
         `End date`,
         `Start time`,
         `End time`,
         Duration)
data_T_summary <- data_T_summary %>%
  select(Project, Description, Duration)

# move long column so printing is better
data_Q_activity <-
  data_Q_activity %>% relocate(Name, .after = Category)

data_T_time <- data_T_time %>%
  mutate(Minutes = seconds(Duration) %>% as.numeric() / 60)
data_T_summary <- data_T_summary %>%
  mutate(Minutes = seconds(Duration) %>% as.numeric() / 60)
# data_Q_activity$Category %>% unique()
```

```{r}
## Add labels

productive <- c("Development", "Documents & Writing", "Reference & Learning", "Email", "Management", "Audio/Video Production")

neutral <- c("Uncategorized", "File Management", "Search", "Utilities & Services", "Messaging")

data_Q_activity <- data_Q_activity %>% 
  mutate(
    Type = case_when(
      Category %in% productive ~ "Productive",
      Category %in% neutral ~ "Neutral",
      TRUE ~ "Distracting"
    )
  )
```

## Initial look at Qbserve data

```{r}
categories <- data_Q_activity %>%
  group_by(Category) %>%
  summarise(n = n(),
            Min = sum(Minutes), Type) %>%
  arrange(-Min)
# categories

app_usage <- data_Q_activity %>%
  group_by(App) %>%
  summarise(n = n(),
            Min = sum(Minutes),
            Type) %>%
  filter(Min > 5) %>%
  arrange(-Min)
# app_usage

categories %>% ggplot(aes(
  x = reorder(Category, -Min),
  y = Min,
  fill = n
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) +
  ggtitle("Categories")

categories %>% ggplot(aes(
  x = reorder(Category, -Min),
  y = Min,
  fill = Type
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) +
  ggtitle("Categories")

app_usage %>% ggplot(aes(
  x = reorder(App,-Min),
  y = Min,
  fill = n
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) + ggtitle("App Usage")

app_usage %>% ggplot(aes(
  x = reorder(App,-Min),
  y = Min,
  fill = Type
)) +
  geom_col() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) + ggtitle("App Usage")
```


## Initial look at Toggl data

We learn that we can ignore `data_T_summary` since it encodes the same information as `data_T_time`.

```{r}
## Left over to parse
# data_Q_hour
# data_T_time
# data_T_summary

## Get the same information here
data_T_time_summary <- data_T_time %>% 
  group_by(Project, Description) %>% 
  summarise(
    Duration = sum(Duration) %>% hms::as_hms(),
    Minutes = sum(Minutes)
  )

# data_T_summary
# They are the same...
data_T_time$Duration %>% sum() == data_T_summary$Duration %>% sum()
```
First data just around categories.

```{r}
data_T_time_summary %>% 
  ggplot(aes(x = reorder(Project, Minutes), y = Minutes, fill=Description)) +
  geom_col() + ggtitle("Time Summary")
```

Then data more temporally. (Calendar might go here)

```{r}
data_Q_hour
data_T_time
```

## Requirements

- Static visualization
- A legend that explains the encodings used
- 2-3 paragraphs explain your visualization and the insights that you gain about yourself by creating the visualization

I hoped to learn where my time went. Honestly, I already had the data collection heavily habituatilzed so that's why I chose it. Additionally, I partially kept up this record keeping because starting a timer incetivises me to work. In some way, it tells me that work has started.

I also noticed that I will start the timer to match when I start working. I don't know what this means, probably just that it's a habit. Honestly that's just motivated by the aspiration for more complete data.

I think more interesting would be a holistic overview that overlays what I did with my records. This would be calendar data and journaling information although I didn't really do that over this week.


- Overlap (with 5-10m grace) between the two

Honestly, I think I'll do this next part like an art project
I really liked the musical note one
What do I need to encode?

- Matching reports
- Mismatch between reports

- Hours
- Category
  - Subcategory
  
- Sequential time -- calendar and start/end (day of week, part of day)

## D3

```{r}
toggle_year_data <- read_csv("Toggl_time_entries_2020-01-01_to_2020-12-31.csv") %>%
  select(Project,
         Description,
         `Start date`,
         `End date`,
         `Start time`,
         `End time`,
         Duration)

toggle_year_data$Project %>% unique()
data_T_time$Project %>% unique()

toggle_year_data <- toggle_year_data %>%
  # mutate(Minutes = seconds(Duration) %>% as.numeric() / 60)
  mutate(Minutes = (seconds(Duration) %>% as.numeric() / 60) %>% round(7))
```



### Bubble Chart

```{r}
# toggle_year_data$Project %>% unique()
bubble_data <- toggle_year_data %>% 
  group_by(Project) %>% 
  summarise(Time = sum(Minutes))

bubble_data <- toggle_year_data %>% 
  group_by(Description, Project) %>% 
  summarise(Time = sum(Minutes))

write_csv(bubble_data, "bubble_toggl_year.csv")

bubble_data_week <- data_T_time %>% 
  group_by(Description, Project) %>% 
  summarise(Time = sum(Minutes))

write_csv(bubble_data_week, "bubble_toggl_week.csv")
```

## Treemap

```{r}
toggle_year_data %>% mutate(
  name = paste(Project, Description, sep="/"),
)

tree_year <- toggle_year_data %>% group_by(Project, Description) %>% 
  summarise(
    size = sum(Minutes) %>% round(6)
  ) %>% mutate(
    name = paste(Project, Description, sep="/")
  ) %>% select(
    name, size
  )

write_csv(tree_year, "tree_toggl_year.csv")

tree_week <- data_T_time %>% group_by(Project, Description) %>% 
  summarise(
    size = sum(Minutes) %>% round(6)
  ) %>% mutate(
    name = paste(Project, Description, sep="/")
  ) %>% select(
    name, size
  )

write_csv(tree_week, "tree_toggl_week.csv")
```

## Radix

```{r}
# Relevant data:
# toggle_year_data
# data_T_time

toggle_year_data2 <- toggle_year_data %>% rename(
  Start_Date = `Start date`
)

projects <- toggle_year_data2$Project %>% unique()
```


```{r}

radix_data_year <- toggle_year_data2 %>%
  mutate(
    Minutes = Minutes / 60
  ) %>% 
  group_by(Start_Date) %>%
  summarise(
    # n = n(),
    Motivated = sum(Minutes[Project == "Motivated"], na.rm = T),
    N_A = sum(Minutes[Project %>% is.na()], na.rm = T),
    School = sum(Minutes[Project == "School"], na.rm = T),
    Working = sum(Minutes[Project == "Working"], na.rm = T),
    Recreation = sum(Minutes[Project == "Recreation"], na.rm = T),
    Chores = sum(Minutes[Project == "Chores"], na.rm = T),
    Systems = sum(Minutes[Project == "Systems"], na.rm = T),
    Planning = sum(Minutes[Project == "Planning"], na.rm = T),
    Absorb = sum(Minutes[Project == "Absorb"], na.rm = T),
    # total = sum(Minutes),
    # check = sum(Motivated, N_A, School, Working, Recreation, Chores, Systems, Planning, Absorb) %>% round(5) == total %>% round(5)
  )  %>% rename(State = Start_Date)

write_csv(radix_data_year, "radix_data_year.csv")

radix_data_week <- data_T_time %>%
  mutate(
    Minutes = Minutes / 60
  ) %>% 
  group_by(`Start date`) %>%
  summarise(
    # n = n(),
    Motivated = sum(Minutes[Project == "Motivated"], na.rm = T),
    N_A = sum(Minutes[Project %>% is.na()], na.rm = T),
    School = sum(Minutes[Project == "School"], na.rm = T),
    Working = sum(Minutes[Project == "Working"], na.rm = T),
    Recreation = sum(Minutes[Project == "Recreation"], na.rm = T),
    Chores = sum(Minutes[Project == "Chores"], na.rm = T),
    Systems = sum(Minutes[Project == "Systems"], na.rm = T),
    Planning = sum(Minutes[Project == "Planning"], na.rm = T),
    Absorb = sum(Minutes[Project == "Absorb"], na.rm = T),
    # total = sum(Minutes),
    # check = sum(Motivated, N_A, School, Working, Recreation, Chores, Systems, Planning, Absorb) %>% round(5) == total %>% round(5)
  )  %>% rename(State = `Start date`)

write_csv(radix_data_week, "radix_data_week.csv")
```



## End




















